Dysregulation of Cerebral Hemoglobin Content in Malawian Children with Malaria

### 2021-05-14 figures.Rmd
switch suppl fig 1 and 2 order

### Supplementary figure 1: Spearman correlations of NIRS variables 
```{r fig_s1, fig.show = "hold", out.width = "50%", fig.height = 12, fig.width = 15}

@@

**Figure S1.** Shown are the spearman correlations among variables measured by Oxiplex and their associated alpha values. Red indicates a positive correlation; blue indicates a negative correlation.

### Supplementary figure 2: Logistic regression curves of NIRS variables
```{r fig_s2, fig.height = 12}

**Figure S2.** Plotted are the individual logistic regression curves of individual variables tested for their discriminatory power between UM and CM. On the y-axis, 1 represents CM while 0 represents UM. A steeper curve indicates higher discriminatory power

>>>>

### Supplementary figure 1: Logistic regression curves of NIRS variables
```{r fig_s1, fig.height = 12}

**Figure S1.** Plotted are the individual logistic regression curves of individual variables tested for their discriminatory power between UM and CM. On the y-axis, 1 represents CM while 0 represents UM. A steeper curve indicates higher discriminatory power
### Supplementary figure 2: Spearman correlations of NIRS variables 
```{r fig_s2, fig.show = "hold", out.width = "50%", fig.height = 12, fig.width = 15}

@@

**Figure S2.** Shown are the spearman correlations among variables measured by Oxiplex and their associated alpha values. Red indicates a positive correlation; blue indicates a negative correlation.
